Discovering cell type motifs in connectomics data

### 2013-12-01 docs/paper.tex
mouse plot looks great, onto c elegans

Using both the chemical and electrical connectivity (see methods), we determined the underlying clusters explained by connectivity and distance (fig ba). A superficial inspection of the results shows clustering into groups consisting roughly homogeneously of motor neurons, sensory neurons, and interneurons. Closer examination reveals agreement with the classifications originally outlined by Brenner in 1986. 
[create structure that mirrors the mouse retina paragraphs] 
[start paragraph with summary sentence] Motorneuron types AS, DA, and VA, all exclusively postsynaptic, are clustered together, as are motorneuron types VD and DD. VC, DB, and VB also mostly share a cluster. Various head motor neurons, including classes SMD, RMD, and RIM are clustered together. Interneurons with known anatomically-distinct connectivity patterns, such as RIA (2 cells) or AVA (2 cells) are clustered into pure groups. The algorithm even correctly places the single-cell class DVB in a distinct group. Note our clustering does not perfectly recover known groupings -- several combinations of head and sensory neurons are combined, and a difficult-to-explain group of 2 VD, 2 VB, a VA, and a DD neuron are grouped together. [algorithm recovers surprising structure based merely on connectivity even though only 278 cells and not spatially homogeneous]

@@

\subsection{Microprocessor}
To show the applicability of our method to other connectome-style datasets, we obtained the spatial location and interconnectivity of a classic microprocessor, the MOS Technology 6502 used in the original Apple II, Atari, and Commodore 64 (cite datasource). We identified a region of the processor with complex but known structure containing the primary general-purpose registers X, Y, and S (figure).

@@

\subsection {Mouse Retina}
Dense serial electron microscopy of a $VOLUMNE$ in the mouse retina by
\autocite{Helmstaedter2013} yielded a listing of places where neurons
come into contact. There were $number$ cells originally, and selected
the $950$ for which the location of the soma could be reconstruted
from the provided cell plots (soma locations were not provided by the
study's authors in machine-readble form). Ultimately
this left a matrix between the total synapse-like contact area between
all pairs of 950 cells. Area was thresholded at $0.5\mum$, determined
by hand, to yield a 950 $\times$ 950 entry matrix that served as input
to our algorithm. We measured the distance between cells using
the reconstructed soma centers, and used the Logistic-Distance
spatial relation. Hyperprior distributions are shown in \ref{supplemental}.

>>>>

Using both the chemical and electrical connectivity (see methods), we
determined the underlying clusters explained by connectivity and
distance (fig ba). A superficial inspection of the results shows
clustering into groups consisting roughly homogeneously of motor
neurons, sensory neurons, and interneurons. Closer examination reveals
agreement with the classifications originally outlined by Brenner in
1986.  [create structure that mirrors the mouse retina paragraphs]

[start paragraph with summary sentence] Motorneuron types AS, DA, and
VA, all exclusively postsynaptic, are clustered together, as are
motorneuron types VD and DD. VC, DB, and VB also mostly share a
cluster. Various head motor neurons, including classes SMD, RMD, and
RIM are clustered together. Interneurons with known
anatomically-distinct connectivity patterns, such as RIA (2 cells) or
AVA (2 cells) are clustered into pure groups. The algorithm even
correctly places the single-cell class DVB in a distinct group. Note
our clustering does not perfectly recover known groupings -- several
combinations of head and sensory neurons are combined, and a
difficult-to-explain group of 2 VD, 2 VB, a VA, and a DD neuron are
grouped together. [algorithm recovers surprising structure based
merely on connectivity even though only 278 cells and not spatially
homogeneous]

@@

To show the applicability of our method to other connectome-style
datasets, we obtained the spatial location and interconnectivity of a
classic microprocessor, the MOS Technology 6502 used in the original
Apple II, Atari, and Commodore 64 (cite datasource). We identified a
region of the processor with complex but known structure containing
the primary general-purpose registers X, Y, and S (figure).

@@

\subsection {Mouse Retina}
Dense serial electron microscopy of a $VOLUMNE$ in the mouse retina by
\autocite{Helmstaedter2013} yielded a listing of places where neurons
come into contact. There were $number$ cells originally, and selected
the $950$ for which the location of the soma could be reconstruted
from the provided cell plots (soma locations were not provided by the
study's authors in machine-readble form). Ultimately
this left a matrix between the total synapse-like contact area between
all pairs of 950 cells. Area was thresholded at $0.5\mu m$, determined
by hand, to yield a 950 $\times$ 950 entry matrix that served as input
to our algorithm. We measured the distance between cells using
the reconstructed soma centers, and used the Logistic-Distance
spatial relation. Hyperprior distributions are shown in \ref{supplemental}.
